### 2022-03-28 manuscript.tex
Update default.docx [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/c1eb46dca3a6035d359424450c0f133449d977a6.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/c1eb46dca3a6035d359424450c0f133449d977a6/checks
https://github.com/scherzerthesis/thesis/actions/runs/2055507416

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/f0267121860593360a74685cabd155d3e28a67fa/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/f0267121860593360a74685cabd155d3e28a67fa}{scherzerthesis/thesis@f026712}
on March 28, 2022.

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/c1eb46dca3a6035d359424450c0f133449d977a6/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/c1eb46dca3a6035d359424450c0f133449d977a6}{scherzerthesis/thesis@c1eb46d}
on March 28, 2022.
